
# Assignment 1

### 1 Create a data frame

#### Step 1
```{r}
animals <- c("Snake", "Ostrich", "Cat", "Spider")
```
 `animals` is a character vector

#### Step 2
```{r}
num_legs <- c(0, 2, 4, 8)
```

#### Step 3
```{r}
animals_df <- data.frame(animals, num_legs)
animals_df
```

#### Step 4  
Yes, the object and their types are listed in the environment window.
animals_df  |   dataframe 4 obs. of 2 variables
animals     |   character vector
num_legs    |   numerical vector

___

### 2 Check and delete objects

#### Step 1
```{r}
ls() # get list of objects
?ls # check usage of ls
```
`animals`, `num_legs` and `animals_df` are the variables present in environment

#### Step 2
```{r}
?rm # check usage of rm fundtion
rm("num_legs") # remove `num_legs`
ls() # animals_df, animals
```

#### Step 3
```{r}
rm(list = ls()) 
# Remove all variables from the environment. ls() gives the character vector of
# all variables in the environment.
```

___

### 3 Create a data frame in R Scripts

#### Step 0,1,2,3
see `myFirstRScrip.R`

#### Step 4 
Yes, the list of objects in working environment is same as 2#1

___

### 4 Create a data frame in R Markdown

see `MyFirstRMarkdown.rmd`

___

### 5

```{r}
x_vect <- seq(12, 2, -2)
print(x_vect)
```
```{r}
X <- matrix(x_vect, nrow = 2)
print(X)
Y <- matrix(1:4, nrow = 2)
print(Y)
Z <- matrix(seq(4, 10, 2), nrow = 2)
print(Z)

t(Y) # transpose Y
t(Z) # transpose Z

Y+Z # matrix sum
Z+Y # matrix sum

Y %*% Z
Z %*% Y

# Matrix addition is commutative.  
# Matrix multiplication is not commutative

Y %*% X

# Error 
# X %*% Y

# The dimensions of X 2x3 and Y 2x2 do not conform.
# The dimension of colums of multiplicant and dimenstion of rows of multiplier
# should be equal for matrix multiplicatoin.

# Element wise multiplication is commutative
Y * Z
Z * Y


Y_inv <- solve(Y)
Y_inv %*% Y # we get an identity matrix

Y_inv %*% X # product is as expected

```

___

### 6 Writing a function within R

```{r}
my_first_r_func <- function(n) {
  # Takes a number as an input and outputs a number

  stopifnot(is.numeric(n), n %% 1 == 0, n >= 0)
  # Stop if the input is not a non-negative integer.

  acc <- 0
  for (i in 0:n - 1) {
    if(i %% 2 == 0 || i %% 7 == 0) { # Check divisibility
      acc <- acc + i
    }
  }

  return(acc) # return the sum
}

print(my_first_r_func(1000))
```

___

### 7 Further R markdown exercises

see mySecondRScript.R

___

### 8 Commiting and Pushing






